---
title: "counts by employee"
author: "Martin Monkman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

library(cansim)

```



Canadian Business Counts, with employees, December 20221, 2, 3
Frequency: Semi-annual

Table: 33-10-0661-01

Release date: 2023-02-20

Geography: Canada, Province or territory


```{r getdata_emp}

df_counts_emp <- get_cansim("33-10-0661-01")

df_counts_emp <- df_counts_emp %>% 
  janitor::clean_names()

```


Canadian Business Counts, with employees, census metropolitan areas and census subdivisions, December 20221, 2, 3, 4
Frequency: Semi-annual

Table: 33-10-0663-01

Release date: 2023-02-20

Geography: Census subdivision, Census metropolitan area

```{r getdata_csd, eval=FALSE}

df_counts_emp_csd <- get_cansim("33-10-0663-01")

```


## wrangle

Filter for BC and 3 digit NAICS details

* see https://www.statcan.gc.ca/en/subjects/standard/naics/2022/v1/index for NAICS details

```{r}
df_counts_emp_3dig <- df_counts_emp %>% 
  filter(geo == "British Columbia") %>% 
  # filter for 3 digit NAICS codes
  filter(str_detect(classification_code_for_north_american_industry_classification_system_naics, "\\[\\d\\d\\d\\]"))



write_csv(df_counts_emp_3dig, here::here("data_output", "df_counts_emp_3dig.csv"))
  
```


wrangle for manufacturing industries

* NAICS 31-33

* https://www23.statcan.gc.ca/imdb/p3VD.pl?Function=getVD&TVD=1369825&CVD=1369826&CPV=31-33&CST=27012022&CLV=1&MLV=5


```{r}

df_counts_emp_321 <- df_counts_emp %>% 
  filter(geo == "British Columbia") %>% 
  # filter for 3 digit NAICS codes
  filter(str_detect(classification_code_for_north_american_industry_classification_system_naics, "\\[321\\]"))

df_counts_emp_321

write_csv(df_counts_emp_321, here::here("data_output", "df_counts_emp_321.csv"))
```

